Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-07-27 src/tex/ms.tex
further clarify absorbed flux/albedo

The net absorbed stellar fluxes of planets are sensitive to their albedo, which is generally poorly constrained for planets outside the solar system~\citep[e.g.,][]{Angerhausen2015,Parmentier2018a,Mansfield2019}.
Here, we assume global redistribution of incoming flux and a fixed Bond albedo of $0.3$, comparable to Earth's~\citep{Haar1971}.
We do not take into account additional heating sources such as tidal effects~\citep[e.g.,][]{Barnes2013}.

>>>>

The net absorbed stellar \rev{fluxes of planets are a function of intrinsic atmospheric properties such as their albedo, which are} generally poorly constrained for planets outside the solar system~\citep[e.g.,][]{Angerhausen2015,Parmentier2018a,Mansfield2019}.
\rev{For instance, a planet with a high albedo may sustain temperate conditions closer to the star than the same planet with a lower albedo and located further away from the star.}
Here, we assume global redistribution of incoming flux and a fixed Bond albedo of $0.3$, comparable to Earth's~\citep{Haar1971}.
We do not take into account additional heating sources such as tidal effects~\citep[e.g.,][]{Barnes2013}.
